---
title: "SpringFinalRMD"
author: "Hartford Johnson"
date: "12/18/2019"
output: html_document
---

Once everything is saved, run to clear your Global Environment.
```{r}
rm(list = ls())
```

Run this to download the "tidyverse" if you have not done so. It will take a minute or two to download if it is your first time running the code.
```{r}
install.packages("tidyverse")
```

Once "tidyverse is downloaded, run this code to load the packages.
```{r}
library("tidyverse")
```

This will source the function, readying it for use on the CSV folder.
```{r}
source(FunctionSpr.R)
```

This will run the function for the files within the CSV folder. Running this will create a new folder titled "SpringData" with the modified files located within.
```{r}
SpringDat.R("CSV")
```

This will display a table with the data of a single file. While not neccesary to run, this code does provide one of the better looking visuals for this type of data.
```{r}
BROYLES <- read_csv("SpringData/BROYLES.csv")
View(BROYLES)
```